INTELLIGENT SYSTEMS

### 2021-04-14 papers/paper_7.tex
finish 7.4.3

\subsection{EXPERIMENTAL RESULTS}
The experiments are conducted on mixed-noise Gaussian noise and on Gaussian 
plus impulse noise. The indices used to estimate the quality of the restructured
images are the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural 
Similarity Index} (SSIM) \cite{0884882841}.

@@

To test the efficiency of the methods, several images belonging to a 
BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
and $n_2$) with different mixture $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
state of the art.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
        \hline        
        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
        \hline 
        \hline
        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
        \hline
        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
    \label{indexCompare}
\end{table}

>>>>

\subsection{EXPERIMENTAL RESULTS}
The experiments are conducted on mixed-noise Gaussian noise and on Gaussian 
plus impulse noise. The indexs used to estimate the quality of the restructured
images are the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural 
Similarity Index} (SSIM) \cite{0884882841}.

@@

To test the efficiency of the methods, several images belonging to a 
BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
and $n_2$) with different ratios $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
state of the art.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
        \hline        
        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
        \hline 
        \hline
        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
        \hline
        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
    \label{indexCompare}
\end{table}

\subsubsection{Gaussian Noise Plus Impulse Noise}
To remove the “salt and pepper” noise, only one image was used on which 
this type of noise was applied. Also for this type of noise, the evaluation is 
made by changing the mixture ratio r and the sigma standard deviation with 
different values. The work done by the proposed method, compared with the 
other methods, is visible in figure \ref{fig:saltComp}. As for the values obtained of the PSNR 
and SSIM indexs, these are visible in table \ref{GNPINIndex}.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper7/salt.png}
    \centering
    \caption{Image reconstruction under Gaussain noise plus random-valued noise comparison.}
    \label{fig:saltComp}
\end{figure}

\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5$} & \multicolumn{3}{c||}{$\sigma_1=10$} & \multicolumn{3}{c||}{$\sigma_1=15$}\\
        \hline        
        $r\rightarrow$ & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3 & 0.1 & 0.2 & 0.3\\
        \hline 
        \hline
        \multirow{2}{*}{Noisy} & 18.76 & 15.76 & 14.04 & 18.43 & 15.61 & 13.95 & 17.94 & 15.38 & 13.81\\
        & 0.3545 & 0.2290 & 0.1662 & 0.3313 & 0.2216 & 0.1626 & 0.3040 & 0.2109 & 0.1571\\
        \hline
        \multirow{2}{*}{Two-phase\cite{0884882828}} & 25.40 & 24.77 & 24.13 & 24.34 & 23.94 & 23.45 & 23.32 & 23.02 & 22.67\\
        & 0.6599 & 0.6313 & 0.5957 & 0.5116 & 0.4914 & 0.4655 & 0.4224 & 0.4058 & 0.3854\\
        \hline
        \multirow{2}{*}{ACWMF+K-SVD \cite{0884882844}\cite{0884882813}} & 26.07 & 25.27 & 24.54 & 25.50 & 24.91 & 23.13 & 24.64 & 24.19 & 23.67\\
        & 0.7130 & 0.6761 & 0.6333 & 0.5902 & 0.5613 & 0.5291 & 0.4855 & 0.4625 & 0.4414\\
        \hline    
        \multirow{2}{*}{LSM-NLR \cite{0884882826}} & 29.48 & 26.97 & 24.55 & 29.43 & 27.08 & 24.43 & 28.51 & 26.06 & 23.98\\
        & 0.6548 & 0.5774 & 0.4982 & 0.6420 & 0.5646 & 0.4770 & 0.6282 & 0.5458 & 0.4643\\
        \hline
        \multirow{2}{*}{$l_1-l_0$\cite{0884882829}} & 30.45 & 27.75 & 25.95 & 28.45 & 26.59 & 25.34 & 27.33 & 25.69 & 24.55\\
        & 0.8962 & 0.7911 & 0.7312 & 0.7539 & 0.6748 & 0.6293 & 0.6793 & 0.6010 & 0.5744\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{31.06} & \bfseries{30.44} & \bfseries{27.66} & \bfseries{30.97} & \bfseries{29.5} & \bfseries{27.41} & \bfseries{29.74} & \bfseries{28.09} & \bfseries{25.73}\\
        & \bfseries{0.9214} & \bfseries{0.9157} & \bfseries{0.8497} & \bfseries{0.8943} & \bfseries{0.8749} & \bfseries{0.8316} & \bfseries{0.8530} & \bfseries{0.8222} & \bfseries{0.7750}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on one image of some methods.}
    \label{GNPINIndex}
\end{table}

\subsubsection{Realistic Noise Removal}
The model was also tested with the images present in the dataset provided 
in \cite{0884882845}. From the following images only one of their cut out parts is taken 
(Fig \ref{fig:crop}). This time the EM-CNN model was compared with different types 
of existing denoising, including the IRCNN which is adopted by CNN of the 
proposed model. Figure \ref{fig:cropRes} shows the results, in terms of PSNR, obtained on 
each cropped image. From these results it can be seen that the proposed 
model does not always manage to obtain the best result, but in any case its 
PSNR average remains higher than the competing denoisers.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper7/crop.png}
    \centering
    \caption{Cropped real noisy images.}
    \label{fig:crop}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper7/crop result.png}
    \centering
    \caption{PSNR result of different methods on cropped real noisy images.}
    \label{fig:cropRes}
\end{figure}
